Analysis: The Sound of Teaching Music 1

### 2019-10-03 script/RNotebook/articulation.Rmd
remove unnecessary parts
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Main predictions
Participants will exaggerate legato and staccato more while teaching.
Participants will exaggerate forte and piano more while teaching.

@@

# For each individual, each block, each trial
ioi <- aggregate(IOI~SubNr*BlockNr*TrialNr*Condition*Skill, data = df_ioi,
                 FUN = function(x){c(length(x), mean = mean(x), sd = sd(x))})
ioi <- cbind(ioi[,1:5], as.data.frame(ioi[,6]))
# Change colnames
colnames(ioi) <- c("SubNr", "BlockNr", "TrialNr", "Condition", "Skill", "N", "Mean", "SD")

@@

>>>>

### Main predictions
Participants will exaggerate legato and staccato more while teaching.

@@

@@

###########
###########
